Comparing vector-based and ACT-R memory models of tag retrieval:\protect\\User-customized hashtag/tag prediction on Twitter and StackOverflow

### 2013-11-13 writeups/proposal/proposal.tex
foo
Former-commit-id: e24613b98debada3d6ec4daf9468063c1a8d2e5f [formerly 54972aa7434a4c503467d45afebb0209b60da825]
Former-commit-id: 12468cc3313ac3db8cff29479dcaae705b727571

As some preliminary research, I have developed and tested a user-customized model for StackOverflow by modifying the model in \textcite{Stanley2013}.
To incorporate the user's prior tag history into the model, the base-level activation term was modified from the original equation in ACT-R.
$B_{i}$ is based on log odds occurrence, which in turn is based on frequency of tag use, or probability of tag use $p_{i}$.
The change to incorporate user's priors was to compute a weighted average for $p_{i}$,
where the probability of using tag $i$ would range from the global probability ($pGlobal_{i}$) to the user's specific probability ($pUser_{i}$) as the user's total tag count ($count$) increases.
Overall model accuracy improved by 5\% after incorporating the user's prior tag history into the model.

>>>>

As some preliminary research, I have developed and tested a user-customized model for StackOverflow by modifying the model in \textcite{Stanley2013}.
To incorporate the user's prior tag history into the model, the base-level activation term was modified from the original equation in ACT-R.
$B_{i}$ is based on log odds occurrence, which in turn is based on frequency of tag use, or probability of tag use $p_{i}$.
To incorporate a user's prior, a weighted average for $p_{i}$ was used,
where the probability of using tag $i$ ranges from the global probability ($pGlobal_{i}$) to the user's specific probability ($pUser_{i}$) as the user's total tag count increases.
Overall model accuracy improved by 5\% after incorporating the user's prior tag history into the model.
